---
title: 'Twitter treasures #rstats'
author: admin
date: '2020-05-14'
categories:
  - Miscellaneous
tags:
  - R
  - rstats
slug: twitter-treasures
lastmod: '2020-05-14T17:19:09+02:00'
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
---

A list of things I found on the internet and thought to be useful.

### Reduce whitespace in printed lists

```{r}
# create a list
alist <- list(a=1,b=2,c=list(d=1:3, e="hello"))
# regular print
alist
# shorter print
print.simple.list(alist)
```

Source: https://twitter.com/coolbutuseless/status/1259972282421739522?s=20

### Rename columns *inside* `dyplyr::select()` call 

```{r message=FALSE, warning=FALSE}
library(dplyr)
mtcars %>% 
  # select some variables *and* rename one
  select(mpg, cyl, displacement = disp) %>% 
  # look at structure of new object
  glimpse()

```

Source: https://twitter.com/n_a_gilbert/status/1259866258708840452?s=20

### Comment out any step in a pipeline 

```{r}
mtcars %>% 
  # perform some wrangling
  filter(cyl > 4) %>% 
  group_by(cyl) %>% 
  # comment out the last line
    # summarise(mean_wt = mean(wt)) %>% 
  # no problem with identity()
  identity()
```

Source: https://twitter.com/thomas_neitmann/status/1260111985968119808?s=20

### Rename objects/variables/etc. within one `R` chunck only

```
Ctrl + Alt + Shift + M
```

Source: https://twitter.com/sergiouribe/status/1251446686255329283?s=20

### Select text vertically (e.g., `geom_line()` to `geom_point()`)

```
Alt + cursor
```

### Auto-format `R` script/chunk

```
Ctrl + Shift + A
```

### Round to nearest tenth, hundred, etc.

```{r}
round(
  # some vector
  c(1, 5, 6, 90, 11, 27, pi),
  # to -1 decimal = tenth
  digits = -1)
```

Source: https://twitter.com/_ColinFay/status/1250706532762861569?s=20

### Apply function to columns of dataframe

```{r}
library(magrittr)
# expose contents
mtcars %$% lm(mpg ~ disp + hp)
```

### Rename columns in dataframe at the end of a pipeline

```{r}
mtcars %>% 
  # some wrangling
  filter(cyl > 4) %>% 
  # rename variables
  setNames(., 1:dim(.)[2])
```

### Print variable names *cleanly* (i.e., comma separated and without quote marks)

```{r}
# print just the names
paste(colnames(mtcars), collapse = ", ") 
```

Source: https://twitter.com/ludmila_janda/status/1217486240058134528?s=20

### Save output of `R` script/chunk

```{r}
# define output file, specify whether to add to existing output
sink(file="output.txt", append = FALSE)
# run some code
mtcars %>% 
  glimpse()
# save output
sink()
```

Source: https://twitter.com/olivier_klein/status/1203347039133802497?s=20

### Turn off scientific notation (e.g., `5.3e-2` to `0.053`)

```{r}
options(scipen = 999)
```

Source: https://twitter.com/edwardhkennedy/status/1188206942017196032?s=20

### List of datasets in `R`

Source: https://vincentarelbundock.github.io/Rdatasets/datasets.html
